The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-18 dictionary.tex
Corrected typo in thm:autornaught

\begin{theorem}\label{thm:autornaught}
Let $G$ be a smooth, commutative group scheme over $\Fq$.
For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$,
every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
Moreover, $\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$, canonically.
\end{theorem}
\begin{proof} 
For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace étalé attached to $\gqcs{L}$.
Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho_y: \gqcs{L}_y \to \gqcs{L}_y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
\end{proof}

>>>>

\begin{theorem}\label{thm:autornaught}
Let $G$ be a smooth, commutative group scheme over $\Fq$.
For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$,
every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
Moreover, $\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$, canonically.
\end{theorem}
\begin{proof} 
For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace étalé attached to $\gqcs{L}$.
Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
\end{proof}
